Structured Versus Decorated Cospans

### 2020-11-18 cospans.tex
Update cospans.tex
double isomorphism in 3.2

@@

@@

@@

@@

@@

In \cite{BC2}, the first two authors introduce the symmetric monoidal double category of \emph{structured cospans} as a formalism to capture open networks. One of the main goals of this paper is to provide a monoidal double equivalence between this double category and that of \emph{decorated cospans}, described in detail in \cref{DecCospansDoubleCat}. We first recall the double category structured cospans form.

@@

\begin{proof}
This was proved in \cite[Theorems~2.3 \& 3.9]{BC2}. In particular, the double category structure only requires that $\X$ have pushouts, since this is how composition is formed.  The symmetric monoidal structure requires also that $\X$  has binary coproducts and an initial object (and thus all finite colimits), and that $\A$ has and $L$ preserves finite coproducts \cite[Theorem~3.2.3]{CourserThesis}.
\end{proof}

The following theorem establishes the equivalence between structured and decorated cospan double categories under certain conditions.  We denote by $\Rex$ the 2-category of finitely cocomplete categories, finitely cocontinuous functors and natural transformatoins.

@@

We have now laid all the necessary background to formally construct an equivalence between the double category of decorated cospans and the double category of structured cospans, with starting point a symmetric lax monoidal pseudofunctor into $\Cat$.

@@

As a left adjoint, this induced $L$ preserves all colimits that exist between the finitely cocomplete categories $\A$ and $\inta F$, so we can construct the double category of structured cospans $\scsp{L}{\inta F}$ of \cref{SC}. Its objects and vertical morphisms are those of the category $\A$ (as for $\dcsp{F}$ earlier), whereas horizontal 1-cells are now cospans of the form $\cspn{L(a)}{v}{L(b)}{}{}$ in the Grothendieck category $\inta F$ (\cref{def:GrothCat}). Explicitly, they consist of two pairs of morphisms 
\begin{equation}\label{eq:scsphor1cell}
 (a,\bot_a)\xrightarrow{\scalebox{0.7}{\(\begin{cases}i\maps a\to m &\textrm{in }\A \\!\maps F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}\)}}(m,x)\xleftarrow{\scalebox{0.7}{\(\begin{cases}o\maps b\to m &\textrm{in }\A \\!\maps F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}\)}}(b,\bot_b)
\end{equation}
with $x\in F(m)$; recall that the reindexing functors $F(i),F(o)$ preserve all finite colimits across the fibre categories.
Finally, the 2-morphisms of this double category in this context unravel as follows
\begin{displaymath}
 \begin{tikzcd}[row sep=1in,column sep=1.7in,ampersand replacement=\&]
 (a,\bot_a)\ar[r,"{\begin{cases}i\maps a\to m &\textrm{in }\A \\!\maps F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}}"]\ar[d,"{\begin{cases}f\maps a\to a' &\textrm{in }\A \\\chi_a\maps F(f)(\bot_a)\cong \bot_{a'} &\textrm{in }F(a')\end{cases}}"description] \& (m,x) \ar[d,"{\begin{cases}k\maps m\to m' &\textrm{in }\A \\ \tau\maps F(k)(x)\to x' &\textrm{in }F(m')\end{cases}}"description] \& (b,\bot_b)\ar[l,"{\begin{cases}o\maps b\to m &\textrm{in }\A \\!\maps F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}}"']\ar[d,"{\begin{cases}g\maps b\to b' &\textrm{in }\A \\\chi_b\maps F(g)(\bot_b)\cong \bot_{b'} &\textrm{in }F(b')\end{cases}}"description] \\
 (a',\bot_{a'})\ar[r,"{\begin{cases}i'\maps a'\to m' &\textrm{in }\A \\!\maps F(i')(\bot_{a'})\to x' &\textrm{in }F(m')\end{cases}}"'] \& (m',x') \& (b',\bot_{b'})\ar[l,"{\begin{cases}o'\maps b'\to m' &\textrm{in }\A \\!\maps F(o')(\bot_{b'})\to x' &\textrm{in }F(m')\end{cases}}"]
 \end{tikzcd}
\end{displaymath}
where the outside vertical legs come from the definition of $L$ on arrows \cref{eq:Lonarrows}. 
Explicitly, the above square commutativities translate to the conditions $k\circ i=i'\circ f$ and $k\circ o=o'\circ g$ in $\A$, and also to
\begin{gather}\label{eq:Grothcommutativity}
 F(k\circ i)(\bot_a)\cong Fk(Fi(\bot_a))\xrightarrow{Fk(!)}Fk(x)\xrightarrow{\tau}x'= \\
 F(i'\circ f)(\bot_a)\cong Fi'(Ff(\bot_a))\xrightarrow{Fi'(\chi_a)}Fi'(\bot_{a'})\xrightarrow{!}x'\nonumber
\end{gather}
in the fibre category $F(m')$, by composition in the Grothendieck category \cref{eq:compGrothcat}. Since both morphisms emanate from the mapped initial object in $F(m')$ under the finitely cocontinuous reindexing functors, they are the unique such into $x'$ therefore this gives no extra conditions; similarly for the equality including $o,o'$.

Building up to an equivalence of the above described double categories, we now define a double functor
\begin{displaymath}
\lE=(\lE_0,\lE_1)\maps\scsp{L}{\inta F} \longrightarrow\dcsp{F}
\end{displaymath}
which on vertical categories acts as the identity $\lE_0 = \id_{\A}$. Given a horizontal 1-cell in $\scsp{L}{\inta F}$ as in \cref{eq:scsphor1cell}, $\lE_1$ maps it to the decorated cospan $i\maps a\to m\leftarrow b:o$ with decoration $x\in F(m)$,
%Notice that this really is a bijective correspondence since the unique maps from the initial objects in the fibres provide no extra information.
whereas a 2-morphism of $L$-structured cospans as above is mapped to the underlying cospan 2-morphism in $\A$
\begin{displaymath}
\begin{tikzcd}
a\ar[r,"i"]\ar[d,"f"'] & m\ar[d,"k"] & b\ar[l,"o"']\ar[d,"g"] \\
a'\ar[r,"i'"']& m' & b'\ar[l,"o'"]
\end{tikzcd}
\end{displaymath}
in $\A$ along with the map $\tau\maps Fk(x)\to x'$ in $F(m')$, namely an $F$-decorated cospan 2-morphism. 
% Once again, this is a bijective correspondence since, as discussed above, the commutativity \cref{eq:Grothcommutativity} holds automatically by initiality of the domain.
With these definitions, $\lE$ is indeed a (pseudo) double functor as in \cref{def:doublefun}: both $\lE_0$ and $\lE_1$ are functors that appropriately commute with sources and targets, and there exist globular 2-isomorphisms $\lE(M) \odot \lE(N) \simrightarrow\lE(M \odot N)$, $U_{\lE m} \simrightarrow\lE(U_m)$
for any pair of composable horizontal 1-cells $M=\cspn{(a,\bot_a)}{(m,x)}{(b,\bot_b)}{}{}$ and $N=\cspn{(b,\bot_b)}{(n,y)}{(c,\bot_c)}{}{}$ and any object $m$ of $\scsp{L}{\inta F}$. Explicitly, $\mathbb{E}(M)\odot \mathbb{E}(N)$ is given as in \cref{eq:dcospanscomposition} via the pushout cospan and decoration
\begin{equation}\label{eq:1}
 \begin{tikzcd}
  & m+_bn & \\
  a\ar[ur] && b,\ar[ul]
 \end{tikzcd}\qquad
  \mathbf{1}\xrightarrow{x\times y}F(m)\times F(n)\xrightarrow{\phi_{m,n}}F(m+n)\xrightarrow{F(\psi)}F(m+_bn)
\end{equation}
whereas first composing $M$ and $N$ in $\scsp{L}{\inta F}$ using pushouts in $\inta F$ (constructed by \cref{lem:fibrewiselimits}) %!!! Christina: would you like me to write how global pushouts are constructed from fiberwise ones and incorporate it earlier say at \cref{rmk:important} where we do so for initial objects?
produces 
\begin{displaymath}
 \begin{tikzcd}[column sep={.7in,between origins}]
 && (m+_b n,F(\sigma_m)x+_{(\bot_{m+_bn})}F(\sigma_n)y) && \\
 & (m,x) \ar[ur] && (n,y)\ar[ul] \\
 (a,\bot_a)\ar[ur] && (b,\bot_b)\ar[ur]\ar[ul] && (c,\bot_c)\ar[ul]
 \end{tikzcd}
\end{displaymath}
where $\sigma$ are the canonical maps into the pushout. %overusing notation, streamline with earlier
Under $\lE$ this is mapped to the underlying $\A$-cospan $\cspn{a}{m+_bn}{b}{}{}$ with decoration $F(\sigma_m)x+F(\sigma_n)y$ -- since a pushout over an initial object is really a coproduct -- which is isomorphic to \cref{eq:1} due to the following diagram 
\begin{displaymath}
 \begin{tikzcd}
F(m)\times F(n)\ar[rr,"\phi"]\ar[d,"F(\sigma_m)\times F(\sigma_n)"']\ar[dr,phantom,"\cong"] && F(m+n)\ar[d,"F(\psi)"]\ar[d,bend right=50, phantom,"\cong"']\ar[dl,"F(\sigma_m+\sigma_n)"description] \\
F(m+_bn)\times F(m+_bn)\ar[r,"\phi"'] & F\left((m+_bn)+(m+_bn)\right)\ar[r,"F(\nabla)"'] & F(m+_bn)
 \end{tikzcd}
\end{displaymath}
where the bottom composite is the fibrewise coproduct in $F(m+_bn)$ as in \cref{eq:explicitstructure1}. The left-hand side isomorphism is due to pseudonaturality of $\phi$ whereas the right-hand side isomorphism follows from universal properties and pseudofunctoriality of $F$.
Regarding identities, $U_m$ is $\cspn{(m,\bot_m)}{(m,\bot_m)}{(m,\bot_m)}{}{}$ with $1_m$ as the $A$-components and isomorphisms between initial objects in the fibres. So $\lE(U_m)$ is the identity cospan in $A$ together with the `initial decoration' $\bot_m\in F(m)$, and so is $U_{\mathbb{E}(m)}$ as in \cref{eq:UFCsp}.

{\chris IN progress...}

Based on the above description of its mapping, it follows that the strong double functor $\mathbb{E}=(\mathbb{E}_0,\mathbb{E}_1)$ is full, faithful and essentially surjective on objects as per \cref{def:fullfaithful,def:essentiallysurj}. Therefore $\mathbb{E} \maps \scsp{L_F}{\inta F} \to \dcsp{F}$ is a double equivalence, by \cref{ShulDubEquiv}.
Christina: In fact, Christina and Kenny believe it is an isomorphism of double categories! Bijective on all levels of objects and morphisms...should we say?

@@

Next, we show that if both double categories $_L \lCsp(\X)$ and $F\lCsp$ are symmetric monoidal, as they are if both $\A$ and $\X$ have finite colimits, then this equivalence of double categories $\mathbb{E} \maps _L \lCsp(\X) \to F\lCsp$ will be symmetric monoidal. First, note that we have an isomorphism $\epsilon \maps 1_{F\lCsp} \to \mathbb{E}(1_{_L \lCsp(\X)})$ and natural isomorphisms $\mu_{c_1,c_2} \maps \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\X)}$ both of which are given by identities since both double categories $_L \lCsp(\X)$ and $F\lCsp$ have $\A$ as their category of objects and $\mathbb{E}_0=\id_{\A}$. The diagrams utilizing these maps that are required to commute do so trivially.

@@

In \cref{thm:equiv} we gave conditions under which the symmetric monoidal double category of \emph{decorated} cospans $F\lCsp$ is equivalent to the  symmetric monoidal double category of \emph{structured} cospans ${}_L \lCsp(\int F)$.   We now show that under the same conditions we get an equivalence of symmetric monoidal bicategories, and of categories.

\begin{thm} \label{thm:bicat_equiv}
Suppose $\A$ has finite colimits and $F \maps(\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\Rex$ as an ordinary pseudofunctor.    Define the symmetric monoidal bicategory $_L\bCsp(\inta F)$ as in \cref{thm:equiv}.   Then there is an equivalence of symmetric monoidal bicategories
\[      F\bCsp \simeq {}_L \bCsp(\inta F)   \]
of symmetric monoidal categories
\[      F\Csp \simeq {}_L \Csp(\inta F)  . \]
\end{thm}

@@

@@

>>>>

Composing these then gives $\lH(M) \odot \lH(N)$:

@@

\node (D) at (2.25,-0.5) {$d_{\lH(M) \odot \lH(N)} \in F'(H(c_1) +_{H(b)} H(c_2))$};

@@

where $$\hspace{-.4in}\scriptstyle{d_{\lH(M) \odot \lH(N)} \maps 1 \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_M) \times E(d_N)) \phi} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F'(H(c_1)+ H(c_2)) \xrightarrow{F' (J)} F'(H(c_1) +_{H(b)} H(c_2)).}$$
We then have a comparison constraint: $$\lH_{M,N} \maps \lH(M) \odot \lH(N) \xrightarrow{\sim} \lH(M \odot N)$$given by the globular 2-isomorphism:

@@

\node (A) at (0,0.5) {$(\lH(M) \odot \lH(N)) \odot \lH(P)$};
\node (B) at (0,-0.5) {$\lH(M \odot N) \odot \lH(P)$};
\node (C) at (0,-1.5) {$\lH((M \odot N) \odot P)$};
\node (A') at (3,0.5) {$\lH(M) \odot (\lH(N) \odot \lH(P))$};
\node (B') at (3,-0.5) {$\lH(M) \odot \lH(N \odot P)$};
\node (C') at (3,-1.5) {$\lH(M \odot (N \odot P))$};
(A) edge node[left]{$\lH_{M,N} \odot 1$} (B)
(B) edge node[left]{$\lH_{M \odot N,P}$} (C)

@@

(C) edge node [above] {$\lH(a')$} (C')
(B') edge node [right] {$\lH_{M,N \odot P}$} (C')
(A') edge node [right]{$1 \odot \lH_{N,P}$} (B');

@@

In \cite{BC2}, the first two authors introduce the symmetric monoidal double category of \emph{structured cospans} as a formalism to capture open networks. One of the main goals of this paper is to provide a monoidal double isomorphism between this double category and that of \emph{decorated cospans}, described in detail in \cref{DecCospansDoubleCat}. We first recall the double category structured cospans form.

@@

\begin{proof}
This was proved in \cite[Theorems~2.3 \& 3.9]{BC2}. Composition is formed by taking pushouts in $\X$ and identity horizontal 1-cells are $L(a)\xrightarrow{\raisebox{-3pt}[0pt][0pt]{=}}L(a)\xleftarrow{\raisebox{-3pt}[0pt][0pt]{=}}L(a)$. In particular, the double category structure only requires that $\X$ have pushouts, whereas the symmetric monoidal structure also requires that $\X$ has binary coproducts and an initial object (and thus all finite colimits), and that $\A$ has and $L$ preserves finite coproducts \cite[Theorem~3.2.3]{CourserThesis}.
\end{proof}

The following theorem establishes the isomorphism between structured and decorated cospan double categories under certain conditions.  We denote by $\Rex$ the 2-category of finitely cocomplete categories, finitely cocontinuous functors and natural transformatoins.

@@

We have now laid all the necessary background to formally construct an isomorphism between the double category of decorated cospans and the double category of structured cospans, with starting point a symmetric lax monoidal pseudofunctor into $\Cat$.

@@

As a left adjoint, this induced $L$ preserves all colimits that exist between the finitely cocomplete categories $\A$ and $\inta F$, so we can construct the double category of structured cospans $\scsp{L}{\inta F}$ of \cref{SC}. Its objects and vertical morphisms are those of the category $\A$ (as for $\dcsp{F}$ earlier), whereas horizontal 1-cells are now cospans of the form $\cspn{L(a)}{v}{L(b)}{}{}$ in the Grothendieck category $\inta F$ (\cref{def:GrothCat}). Explicitly, they consist of two pairs of morphisms 
\begin{equation}\label{eq:scsphor1cell}
 (a,\bot_a)\xrightarrow{\scalebox{0.7}{\(\begin{cases}i\maps a\to m &\textrm{in }\A \\!\maps F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}\)}}(m,x)\xleftarrow{\scalebox{0.7}{\(\begin{cases}o\maps b\to m &\textrm{in }\A \\!\maps F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}\)}}(b,\bot_b)
\end{equation}
with $x\in F(m)$; recall that the reindexing functors $F(i),F(o)$ preserve all finite colimits across the fibre categories.
Finally, the 2-morphisms of this double category in this context unravel as follows
\begin{equation}\label{eq:2morphismLCspintaF}
 \begin{tikzcd}[row sep=1in,column sep=1.7in,ampersand replacement=\&]
 (a,\bot_a)\ar[r,"{\begin{cases}i\maps a\to m &\textrm{in }\A \\!\maps F(i)(\bot_a)\to x &\textrm{in }F(m)\end{cases}}"]\ar[d,"{\begin{cases}f\maps a\to a' &\textrm{in }\A \\\chi_a\maps F(f)(\bot_a)\cong \bot_{a'} &\textrm{in }F(a')\end{cases}}"description] \& (m,x) \ar[d,"{\begin{cases}k\maps m\to m' &\textrm{in }\A \\ \tau\maps F(k)(x)\to x' &\textrm{in }F(m')\end{cases}}"description] \& (b,\bot_b)\ar[l,"{\begin{cases}o\maps b\to m &\textrm{in }\A \\!\maps F(o)(\bot_b)\to x &\textrm{in }F(m)\end{cases}}"']\ar[d,"{\begin{cases}g\maps b\to b' &\textrm{in }\A \\\chi_b\maps F(g)(\bot_b)\cong \bot_{b'} &\textrm{in }F(b')\end{cases}}"description] \\
 (a',\bot_{a'})\ar[r,"{\begin{cases}i'\maps a'\to m' &\textrm{in }\A \\!\maps F(i')(\bot_{a'})\to x' &\textrm{in }F(m')\end{cases}}"'] \& (m',x') \& (b',\bot_{b'})\ar[l,"{\begin{cases}o'\maps b'\to m' &\textrm{in }\A \\!\maps F(o')(\bot_{b'})\to x' &\textrm{in }F(m')\end{cases}}"]
 \end{tikzcd}
\end{equation}
where the outside vertical legs come from the definition of $L$ on arrows \cref{eq:Lonarrows}. 
Explicitly, the above square commutativities translate to the conditions $k\circ i=i'\circ f$ and $k\circ o=o'\circ g$ in $\A$, and also to
\begin{gather}\label{eq:Grothcommutativity}
 F(k\circ i)(\bot_a)\cong Fk(Fi(\bot_a))\xrightarrow{Fk(!)}Fk(x)\xrightarrow{\tau}x'= \\
 F(i'\circ f)(\bot_a)\cong Fi'(Ff(\bot_a))\xrightarrow{Fi'(\chi_a)}Fi'(\bot_{a'})\xrightarrow{!}x'\nonumber
\end{gather}
in the fibre category $F(m')$, by composition in the Grothendieck category \cref{eq:compGrothcat}. Since both morphisms emanate from the mapped initial object in $F(m')$ under the finitely cocontinuous reindexing functors, they are the unique such into $x'$ therefore this gives no extra conditions; similarly for the equality including $o,o'$.

Building up to an isomorphism of the above described double categories, we now define a double functor
\begin{displaymath}
\lE=(\lE_0,\lE_1)\maps\scsp{L}{\inta F} \longrightarrow\dcsp{F}
\end{displaymath}
which on vertical categories acts as the identity $\lE_0 = \id_{\A}$. Given a horizontal 1-cell in $\scsp{L}{\inta F}$ as in \cref{eq:scsphor1cell}, $\lE_1$ maps it to the decorated cospan $i\maps a\to m\leftarrow b:o$ with decoration $x\in F(m)$,
whereas a 2-morphism of $L$-structured cospans as above is mapped to the underlying cospan 2-morphism in $\A$
\begin{displaymath}
\begin{tikzcd}
a\ar[r,"i"]\ar[d,"f"'] & m\ar[d,"k"] & b\ar[l,"o"']\ar[d,"g"] \\
a'\ar[r,"i'"']& m' & b'\ar[l,"o'"]
\end{tikzcd}
\end{displaymath}
in $\A$ along with the map $\tau\maps Fk(x)\to x'$ in $F(m')$, namely an $F$-decorated cospan 2-morphism. 
With these definitions, $\lE$ is indeed a (pseudo) double functor as in \cref{def:doublefun}: both $\lE_0$ and $\lE_1$ are functors that appropriately commute with sources and targets, and there exist globular 2-isomorphisms $\lE(M) \odot \lE(N) \simrightarrow\lE(M \odot N)$, $U_{\lE m} \simrightarrow\lE(U_m)$
for any pair of composable horizontal 1-cells $M=\cspn{(a,\bot_a)}{(m,x)}{(b,\bot_b)}{}{}$ and $N=\cspn{(b,\bot_b)}{(n,y)}{(c,\bot_c)}{}{}$ and any object $m$ of $\scsp{L}{\inta F}$. Explicitly, $\mathbb{E}(M)\odot \mathbb{E}(N)$ is given as in \cref{eq:dcospanscomposition} via the pushout cospan and decoration
\begin{equation}\label{eq:1}
 \begin{tikzcd}
  & m+_bn & \\
  a\ar[ur] && b,\ar[ul]
 \end{tikzcd}\qquad
  \mathbf{1}\xrightarrow{x\times y}F(m)\times F(n)\xrightarrow{\phi_{m,n}}F(m+n)\xrightarrow{F(\psi)}F(m+_bn)
\end{equation}
whereas first composing $M$ and $N$ in $\scsp{L}{\inta F}$ using pushouts in $\inta F$ (constructed by \cref{lem:fibrewiselimits}) %!!! Christina: would you like me to write how global pushouts are constructed from fiberwise ones and incorporate it earlier say at \cref{rmk:important} where we do so for initial objects?
produces 
\begin{displaymath}
 \begin{tikzcd}[column sep={.7in,between origins}]
 && (m+_b n,F(\sigma_m)x+_{(\bot_{m+_bn})}F(\sigma_n)y) && \\
 & (m,x) \ar[ur] && (n,y)\ar[ul] \\
 (a,\bot_a)\ar[ur] && (b,\bot_b)\ar[ur]\ar[ul] && (c,\bot_c)\ar[ul]
 \end{tikzcd}
\end{displaymath}
where $\sigma$ are the canonical maps into the pushout. %overusing notation, streamline with earlier
Under $\lE$ this is mapped to the underlying $\A$-cospan $\cspn{a}{m+_bn}{b}{}{}$ with decoration $F(\sigma_m)x+F(\sigma_n)y$, since a pushout over an initial object is really a coproduct. That decoration is isomorphic to that of \cref{eq:1} due to the following diagram 
\begin{displaymath}
 \begin{tikzcd}
F(m)\times F(n)\ar[rr,"\phi"]\ar[d,"F(\sigma_m)\times F(\sigma_n)"']\ar[dr,phantom,"\cong"] && F(m+n)\ar[d,"F(\psi)"]\ar[d,bend right=50, phantom,"\cong"']\ar[dl,"F(\sigma_m+\sigma_n)"description] \\
F(m+_bn)\times F(m+_bn)\ar[r,"\phi"'] & F\left((m+_bn)+(m+_bn)\right)\ar[r,"F(\nabla)"'] & F(m+_bn)
 \end{tikzcd}
\end{displaymath}
where the bottom composite is the fibrewise coproduct in $F(m+_bn)$ as in \cref{eq:explicitstructure1}. The left-hand side isomorphism is due to pseudonaturality of $\phi$ whereas the right-hand side isomorphism follows from universal properties and pseudofunctoriality of $F$.
Regarding identities, the identity horizontal 1-cell $U_m$ in $_L\lCsp(\inta F)$ is $\cspn{(m,\bot_m)}{(m,\bot_m)}{(m,\bot_m)}{}{}$ with $1_m$ as the $A$-component and isomorphisms between initial objects in the fibres. Thus $\lE(U_m)$ is the identity cospan in $A$ together with the `initial decoration' $\bot_m\in F(m)$, and so is $U_{\mathbb{E}(m)}$ as in \cref{eq:UFCsp}. %Do we want to check that E is a double functor one last time?

In fact, the double functor $\lE\maps _L\lCsp(\inta F)\to\dcsp{F}$ as defined above is bijective on objects and vertical 1-cells (trivially as an identity functor), and is also bijective on horizontal 1-cells and on 2-morphisms. Indeed, for \cref{eq:scsphor1cell}, the unique maps from the initial objects in the fibres provide no actual extra information, and similarly for 2-cells all extra data in \cref{eq:2morphismLCspintaF} is uniquely determined and \cref{eq:Grothcommutativity} holds automatically as discussed above. As a result, we have a double isomorphism $$\scsp{L_F}{\inta F} \cong \dcsp{F}.$$

@@

Next, we show that if both double categories $_L \lCsp(\X)$ and $F\lCsp$ are symmetric monoidal, as they are if both $\A$ and $\X$ have finite colimits, then this isomorphism of double categories $\mathbb{E} \maps _L \lCsp(\X) \to F\lCsp$ will be symmetric monoidal. First, note that we have an isomorphism $\epsilon \maps 1_{F\lCsp} \to \mathbb{E}(1_{_L \lCsp(\X)})$ and natural isomorphisms $\mu_{c_1,c_2} \maps \mathbb{E}(c_1) \otimes \mathbb{E}(c_2) \to \mathbb{E}(c_1 \otimes c_2)$ for every pair of objects $c_1,c_2 \in {_L \mathbb{C} \textnormal{sp}(\X)}$ both of which are given by identities since both double categories $_L \lCsp(\X)$ and $F\lCsp$ have $\A$ as their category of objects and $\mathbb{E}_0=\id_{\A}$. The diagrams utilizing these maps that are required to commute do so trivially.

@@

In \cref{thm:equiv} we gave conditions under which the symmetric monoidal double category of \emph{decorated} cospans $F\lCsp$ is isomorphic to the  symmetric monoidal double category of \emph{structured} cospans ${}_L \lCsp(\int F)$.   We now show that under the same conditions we get an isomorphism of symmetric monoidal bicategories, and of categories.

\begin{thm} \label{thm:bicat_equiv}
Suppose $\A$ has finite colimits and $F \maps(\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\Rex$ as an ordinary pseudofunctor.    Define the symmetric monoidal bicategory $_L\bCsp(\inta F)$ as in \cref{thm:equiv}.   Then there is an isomorphism of symmetric monoidal bicategories
\[      F\bCsp \simeq {}_L \bCsp(\inta F)   \]
of symmetric monoidal categories
\[      F\Csp \simeq {}_L \Csp(\inta F)  . \]
\end{thm}

@@

IN THE PROOF ABOVE, WE ACTUALLY POTENTIALLY NEED SYMMETRY. DOES IT FOLLOW?

@@

WE NEED TO SAY BRIEFLY WHAT A DOUBLE ISOMORPHISM IS.
